Parameter estimation

### 2023-03-09 SFE-article/Sections/Low_mach_number_expansion.tex
09.03

	The equations \ref{EQ: CompressibleEuler} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case. We rescale the time variable, considering finally

	{\footnotesize
		\begin{equation*}
			\rho_\zeta 	= \rho\left( z, t/M_a \right), \quad
			V_\zeta 	= \cfrac{1}{\zeta} V\left( z, t/M_a \right) \quad
			T_\zeta 	= T\left( z, t/M_a \right),  \quad 
			k_\zeta 	= \zeta k(\rho_f, T) 
		\end{equation*} 
	}

@@

	{\footnotesize
		\begin{align*}
			\cfrac{\partial \left( \rho_\zeta A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_\zeta A_f V_\zeta \right)}{\partial z} = 0 \\
			\cfrac{\partial \left( \rho_\zeta A_f V_\zeta \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_\zeta V_\zeta A_f V_\zeta \right)}{\partial z} + \cfrac{A_f}{M_a^2} \cfrac{\partial P_\zeta}{\partial z} = 0\\
			\cfrac{\partial \left( \rho_\zeta e_\zeta A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_\zeta e_\zeta V_\zeta A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_\zeta}{\partial z} \right) + P_\zeta \cfrac{\partial A_f V_\zeta}{\partial z} = 0
		\end{align*}
	}

@@

	{\footnotesize
		\begin{align*}
			P_\zeta 	& = P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3) \\
			\rho_\zeta 	& = \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \\
			V_\zeta 	& = V_0		+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
			T_\zeta 	& = T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
			e_\zeta 	& = e_0 	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
		\end{align*}
	}

@@

	 {\footnotesize
	 	\begin{align*}
	 		& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \right)}{\partial t} + \\
	 		&+ \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
	 	\end{align*}
	 }

@@

		 {\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_0 A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_0 A_f V_0 \right)}{\partial z} = 0
		\end{equation}
	}

@@

	{\footnotesize
		\begin{align*}
		 & \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial t} + \\
		 &+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( V_0	+ V_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
		 &+ A_f \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2}	+ \cfrac{P_1 \zeta}{M_a^2}	+ \cfrac{P_2 \zeta^2}{M_a^2} + \mathcal{O}(\zeta^3) \right)
		\end{align*}
	}

@@

	The simplification of the $P_0$ in the momentum equation comes from the fact that $P_0$ is independent of $z$. The term related to $P_2$ and higher order terms become zero at the limit of $M_a \rightarrow 0$. The momentum equation become

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left( \rho_0 A_f V_0 \right) }{\partial t}	+ \cfrac{\partial \left( \rho_0 V_0 A_f V_0 \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{align*}
			& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right)}{\partial t} + \\
			&+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
			&+ \cfrac{\partial}{\partial z} \left( k \cfrac{\partial }{\partial z} \left( T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) + \\
			&- \left(  P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3)  \right) \cfrac{\partial \left( A_f \left( V_0 + V_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
		\end{align*}
	}

@@

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left( \rho_0 e_0 A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_0 e_0 V_0 A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_0}{\partial z} \right) + P_0 \cfrac{\partial A_f V_0}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{align*}
			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_f A_f V \right)}{\partial z} = 0 \\
			\cfrac{\partial \left( \rho_f A_f V \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_f V A_f V \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0\\
			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_f e V A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{align*}
	}

@@

	{\footnotesize
		\begin{equation*}
			 \rho A_f \left( \cfrac{\partial e }{\partial t} + V \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f V A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{equation*}
		\rho A_f \left( \cfrac{\partial e }{\partial t} + V \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{equation*}
			\rho A_f C_v \left( \cfrac{\partial T }{\partial t} + V \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{equation*}
			\lim_{\Delta T \rightarrow 0_+} \rho A_f C_v \left( \cfrac{\partial T }{\partial t} + V \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{equation}
			\cfrac{\partial A_f V}{\partial z} = 0
			\label{EQ: Incompressibility_Condition_Ideal_IsoThermal}
		\end{equation}
	}

	In one-dimensional case, the equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f V) = 0$, which known as the incompressibility condition (\citet{Lions2013}).

>>>>

	The equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case. We rescale the time variable, considering finally

	{\footnotesize
		\begin{align*}
			\rho_\zeta 	&= \rho\left( z, t/M_a \right), \quad
			v_\zeta 	= \cfrac{1}{\zeta} v\left( z, t/M_a \right) \\ 
			T_\zeta 	&= T\left( z, t/M_a \right),  \quad 
			k_\zeta 	= \zeta k(\rho_f, T) 
		\end{align*} 
	}

@@

	{\footnotesize
		\begin{align*}
			\cfrac{\partial \left( \rho_\zeta A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_\zeta A_f v_\zeta \right)}{\partial z} = 0 \\
			\cfrac{\partial \left( \rho_\zeta A_f v_\zeta \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_\zeta v_\zeta A_f v_\zeta \right)}{\partial z} + \cfrac{A_f}{M_a^2} \cfrac{\partial P_\zeta}{\partial z} = 0\\
			\cfrac{\partial \left( \rho_\zeta e_\zeta A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_\zeta e_\zeta v_\zeta A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_\zeta}{\partial z} \right) + P_\zeta \cfrac{\partial A_f v_\zeta}{\partial z} = 0
		\end{align*}
	}

@@

	{\footnotesize
		\begin{align*}
			P_\zeta 	& = P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3) \\
			\rho_\zeta 	& = \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \\
			v_\zeta 	& = v_0		+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
			T_\zeta 	& = T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
			e_\zeta 	& = e_0 	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
		\end{align*}
	}

@@

	 {\footnotesize
	 	\begin{align*}
	 		& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \right)}{\partial t} + \\
	 		&+ \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
	 	\end{align*}
	 }

@@

		 {\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_0 A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_0 A_f v_0 \right)}{\partial z} = 0
		\end{equation}
	}

@@

	{\footnotesize
		\begin{align*}
		 & \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial t} + \\
		 &+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( v_0	+ v_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
		 &+ A_f \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2}	+ \cfrac{P_1 \zeta}{M_a^2}	+ \cfrac{P_2 \zeta^2}{M_a^2} + \mathcal{O}(\zeta^3) \right)
		\end{align*}
	}

@@

	The simplification of the $P_0$ in the momentum equation comes from the fact that $P_0$ is independent of $z$. As it was presented above, the thermodynamical pressure moves with speed of sound, and any perturbation propagates instantaneously. The term related to $P_2$ and higher order terms become zero at the limit of $M_a \rightarrow 0$. The momentum equation become

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left( \rho_0 A_f v_0 \right) }{\partial t}	+ \cfrac{\partial \left( \rho_0 v_0 A_f v_0 \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{align*}
			& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right)}{\partial t} + \\
			&+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
			&+ \cfrac{\partial}{\partial z} \left( k \cfrac{\partial }{\partial z} \left( T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) + \\
			&- \left(  P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3)  \right) \cfrac{\partial \left( A_f \left( v_0 + v_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
		\end{align*}
	}

@@

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left( \rho_0 e_0 A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_0 e_0 v_0 A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_0}{\partial z} \right) + P_0 \cfrac{\partial A_f v_0}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{align*}
			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} = 0 \\
			\cfrac{\partial \left( \rho_f A_f v \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_f v A_f v \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0\\
			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_f e v A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
		\end{align*}
	}

@@

	{\footnotesize
		\begin{equation*}
			 \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{equation*}
		\rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{equation*}
			\rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{equation*}
			\lim_{\Delta T \rightarrow 0_+} \rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
		\end{equation*}
	}

@@

	{\footnotesize
		\begin{equation}
			\cfrac{\partial A_f v}{\partial z} = 0
			\label{EQ: Incompressibility_Condition_Ideal_IsoThermal}
		\end{equation}
	}

	In one-dimensional case, the equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f v) = 0$, which known as the incompressibility condition (\citet{Lions2013}).

		A general formulation the internal energy for a real gas is:

	{\footnotesize
		\begin{equation*}
			de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{V_m}\right]dv_m
	\end{equation*} }

	where $v_m$ is the molar volume.

	The internal energy is a function of two intensive properties, in this case $T$ and $v_m=1/\rho_f$. But, in the case of an ideal gas, the equation of state is such that the second term in this equation is identically equal to zero. So the ideal gas is a special case in which the molar internal energy is a function only of temperature. For Peng-Robinson equation of state, the internal energy is defined as

	{\footnotesize
	\begin{equation*}
		e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
	\end{equation*} }

	Assuming constant temperature and pressure along space and in time:

	{\footnotesize
		\begin{equation*}
			\lim_{\Delta T, \Delta P \rightarrow 0_+ } \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0 \rightarrow \cfrac{\partial A_f v}{\partial z} = 0
		\end{equation*}
	}

	It can be deduce that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure. Moreover, the incompressibility condition $div(A_fV)=0$ is obtained.

	Assuming an arbitrary function $\hat{P}$, which describe the total pressure, the dimensional momentum equation can be written as

	{\footnotesize
		\begin{equation*}
			V \underbrace{ \left( \cfrac{\partial \rho_f A_f}{\partial t} + \cfrac{\rho_f v A_f}{\partial z} \right) }_{Continuity~equation} + \rho_f A_f \cfrac{\partial v}{\partial t} + \rho_f v A_f \cfrac{\partial v}{\partial z} = - A_f \cfrac{\partial \hat{P}}{\partial z}
		\end{equation*}
	}

	From the incompressibility conditions we can deduce that

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial A_f v}{\partial z} = 0 \rightarrow A_f \cfrac{\partial v}{\partial z} = - v \cfrac{\partial A_f}{\partial z}
		\end{equation*}
	}

	By combining both above equations, assuming that $\partial v / \partial t = 0$:

	{\footnotesize
		\begin{equation*}
			\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} = \cfrac{\partial \hat{P}}{\partial z} \rightarrow \int	\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int \cfrac{\partial\hat{P}}{\partial z} dz
		\end{equation*}
	}

	The l.h.s integral can be solved by assuming $\rho_f$ is constant and introducing superficial velocity $u_s=A_f v$

	{\footnotesize
		\begin{align*}
			& \int	\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int	\cfrac{\rho_f v^2}{A_f} \cfrac{A_f^2}{A_f^2} \cfrac{\partial A_f}{\partial z} dz \\
			&= \rho_f u_s^2  \int \cfrac{1}{A_f^3} \cfrac{\partial A_f}{\partial z} dz = - \cfrac{\rho_f u_s^2}{2 \Delta A_f^2} = - \cfrac{\rho_f \Delta v^2}{2} \\
			& \int \cfrac{\partial \hat{P}}{\partial z} dz = \Delta \hat{P}
		\end{align*}
	}

	The final form of the momentum equation corresponds to the Bernoulli's principle

	{\footnotesize
		\begin{equation*}
			\Delta \hat{P} = - \cfrac{\rho_f \Delta v^2}{2} \xrightarrow[]{P_0 = \text{const}} \Delta M_a^2 P_1 = - \cfrac{\rho_f \Delta v^2}{2}
		\end{equation*}
	}

	The Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-section at steady-state. Moreover, if the flow velocity is relatively low and so all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic. The effect of this is that $\partial \rho / \partial P = 0$. In other words, the small changes in pressure due to flow velocity changes do not change the density. This has a secondary effect -- the speed of sound in the fluid is $\partial P/\partial \rho = \infty$	in this instance. So there is an infinite speed of sound, which makes the equations elliptic in nature. It can be deduced that at the isothermal conditions the density in the system propagates with the same speed as pressure due to the fact that they are both connected through the equation of state.
